Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
Improve introduction

The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners. We would like to carefully analyze the credibility of these domains in the real world and evaluate the worth of FF-Replan vs a state of the art probabilistic planner: Gourmand \cite{kolobov2012gourmand}.

>>>>

Since the first incorporation of the International Probabilistic Planning
Competition (IPPC), it has undergone radical changes. Dominating planners
of previous incorporations had a strong focus on goal-oriented MDPs,
determinizing and using powerful classical planners (e.g. FF
\cite{Hoffmann01theff}) and replanning. New benchmarks have demonstrated
weaknesses in existing solution techniques.

Little and Thi\'ebaux have developed a baseline test in
\cite{little2007probvsreplan} to evaluate the IPC-5 problems. This
test determines if a planning problem is `probabilistically interesting'.
Problems that fail this test are classical planning problems in disguise.
Knowing this it is easy to design a problem where a replanner performs badly
or incredibly well.

The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
which can design domains that are more probabilistically interesting. The top
performers were PROST \cite{keller2012prost} and Glutton
\cite{kolobov2012glutton}.

While it is interesting to make problems harder and invent better planning
algorithms to solve those probabilistic complex problems, one must not forget
if the problem makes sense in the real world.

The main contribution of this paper is an evaluation of the domains used in
IPPC-11 and see if they can be adjusted so they fail the baseline test for
probabilistic interestingness, which might make them more suitable for
replanning planners.
